The Impact of Alternation

### 2017-05-10 draft.tex
ok

  \For{$m \in N$ such that $n \prec^* m$ and $n$ is not an ancestor of $m$}
  \Comment{close $n$}

  \If{$\Lambda(n) \models \Lambda(m)$}

  \State $\lhd \leftarrow \lhd \setminus \set{ (p,q) \in \lhd \mid
    \text{$q$ is a successor of $n$}}$

  \State $\lhd \leftarrow \lhd \cup \set{(n,m)}$

  \State {\bf goto} \ref{ln:not-covered}

@@

  \State let $\rootNode,n_1,\ldots,n_k,n$ be the sequence of nodes from $\rootNode$ to $n$

@@

@@

  \EndWhile  
\end{algorithmic}}
\caption{\impact~ for ADA Emptiness}
\label{alg:impact}
\end{algorithm}

The execution of Algorithm \ref{alg:impact} consists of three
phases\footnote{These phases correspond to the \textsc{Close},
  \textsc{Refine} and \textsc{Expand} procedures from the original
  description of \impact~\cite{mcmillan06}.}: \emph{close},
\emph{refine} and \emph{expand}.

>>>>

  \State $\Call{Close}{n}$
  \label{ln:close-worklist}

@@

  \State let $\rootNode,n_1,\ldots,n_k,n_{k+1}=n$ be the sequence of nodes from $\rootNode$ to $n$

@@

  \State $\Call{Close}{n_i}$

@@

  \EndWhile  
\end{algorithmic}

\begin{algorithmic}[1]
\Function{Close}{$x$}

\For{$y \in N$ such that $x \prec^* y$ and $x$ is not an ancestor of $y$}

\If{$\Lambda(x) \models \Lambda(y)$}

\State $\lhd \leftarrow \left(\lhd \setminus \set{ (p,q) \in \lhd \mid
  \text{$q$ is a successor of $x$}}\right) \cup \set{(x,y)}$

\State {\bf return}

\EndFunction
\end{algorithmic}}
\caption{\impact~ for ADA Emptiness}
\label{alg:impact}
\end{algorithm}

The execution of Algorithm \ref{alg:impact} consists of three
phases\footnote{These phases correspond to the \textsc{Close},
  \textsc{Refine} and \textsc{Expand} procedures from the original
  description of \impact~\cite{mcmillan06}.}: \emph{close},
\emph{refine} and \emph{expand}. When a node $n$ is removed from the
worklist, it is first closed (line \ref{ln:close-worklist}) by finding
a lexicographically bigger node $m$ such that $\Lambda(n) \models
\Lambda(m)$, if one exists, and adding $(n,m)$ to $\lhd$. As in
Algorithm \ref{alg:predabs}, the intuition is that all successors of
$n$ are covered by the successors of $m$, thus for any feasible
counterexample that can be discovered from $n$ there exists a feasible
counterexample stemming in $m$, and we do not need to process $n$
further. If $n$ has not been covered in the close phase, we check if
it is the endpoint of a counterexample candidate, which can only be
the case
